2020 Geomarkets + CBSA

### 2025-11-19 scripts/geomarket_cbsa.Rmd
add missing EPS shapes

>>>>

# Other

Not in `connections-geographies-cb.pdf`, so base the shapes off the original zip code EPS geomarkets. (See: `cb_geo/data/eps_market/eps_shapes.RData` and `cb_geo/data/eps_market/eps_names.csv`)

## Hawaii

- **HI 1**: Island of Oahu
- **HI 2**: Remaining Hawaiian Islands

```{r}
plot_map(
  c('HI 1', 'HI 2')
)
```

## New York

- **NY 1**: Southern Tier West
- **NY 2**: Erie Co
- **NY 3**: Genesee Valley & N. Frontier
- **NY 4**: Rochester & Monroe Co
- **NY 5**: Finger Lakes Region
- **NY 6**: Central New York
- **NY 7**: Saint Lawrence Valley
- **NY 8**: Adirondacks
- **NY 9**: Tri Cities
- **NY10**: Central Hudson Valley
- **NY11**: Catskills
- **NY12**: Southern Tier East
- **NY13**: Rockland Co

```{r}
plot_map(
  c('NY 1', 'NY 2', 'NY 3', 'NY 4', 'NY 5', 'NY 6', 'NY 7', 'NY 8', 'NY 9', 'NY10', 'NY11', 'NY12', 'NY13')
)
```

## Long Island

- **NY16**: Southern Nassau Co
- **NY17**: Northern Nassau Co
- **NY18**: Central Nassau Co
- **NY19**: Northwest Suffolk Co
- **NY20**: Southwest Suffolk Co
- **NY21**: East Suffolk Co

```{r}
plot_map(
  c('NY16', 'NY17', 'NY18', 'NY19', 'NY20', 'NY21')
)
```

## NY, NY

- **NY14**: Staten Island
- **NY15**: Westchester Co
- **NY22**: Southeast Brooklyn
- **NY23**: West Brooklyn
- **NY24**: Northeast Brooklyn
- **NY25**: East Bronx
- **NY26**: West Bronx
- **NY27**: Manhattan
- **NY28**: South Queens
- **NY29**: Northwest Queens
- **NY30**: Northeast Queens

```{r}
plot_map(
  c('NY14', 'NY15', 'NY22', 'NY23', 'NY24', 'NY25', 'NY26', 'NY27', 'NY28', 'NY29', 'NY30')
)
```
